Spatial variation of coronal Fourier power spectra

### 2016-08-02 tex/paper2/paper2.tex
BIC plots, with Python 3 compliance and updated paper

\begin{figure}
\label{fig:spatialdistribution:preference}
\centerline{
\epsscale{0.8}\plottwo{paper2_six_euv_disk_1.5_94.exact_map.six_euv.eps}{paper2_six_euv_disk_1.5_131.exact_map.six_euv.eps}
}
\centerline{
\epsscale{0.8}\plottwo{paper2_six_euv_disk_1.5_171.exact_map.six_euv.eps}{paper2_six_euv_disk_1.5_193.exact_map.six_euv.eps}
}
\centerline{
\epsscale{0.8}\plottwo{paper2_six_euv_disk_1.5_211.exact_map.six_euv.eps}{paper2_six_euv_disk_1.5_335.exact_map.six_euv.eps}
}
\caption{Spatial distribution of model preference.}
\end{figure}

>>>>

\begin{figure}
\label{fig:spatialdistribution:preference}
\centerline{
\epsscale{0.8}\plottwo{spatial_distrib.paper2_six_euv_disk_1.5_171_six_euv.BIC.6.0.with_mask.eps}{spatial_distrib.paper2_six_euv_disk_1.5_171_six_euv.BIC.6.0.with_mask.eps}
}
\centerline{
\epsscale{0.8}\plottwo{spatial_distrib.paper2_six_euv_disk_1.5_171_six_euv.BIC.6.0.with_mask.eps}{spatial_distrib.paper2_six_euv_disk_1.5_171_six_euv.BIC.6.0.with_mask.eps}
}
\centerline{
\epsscale{0.8}\plottwo{spatial_distrib.paper2_six_euv_disk_1.5_171_six_euv.BIC.6.0.with_mask.eps}{spatial_distrib.paper2_six_euv_disk_1.5_171_six_euv.BIC.6.0.with_mask.eps}
}
\caption{Spatial distribution of model preference. Blue pixels indicate a strong preference for Model 2.  Cyan pixels indicate a strong preference for Model 1.  Black pixels indicate that neither Model 1 or Model 2 could be fit to the data. The remaining pixels show a weaker preference for either Model 1 or Model 2.  The location of the sunspot is indicated by the white contour.}
\end{figure}
